Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-09-24 main_new.tex
updates

Two missions, Survey 1 and 2, were run successively from 11:00 AM to 01:00 PM, with a short break in between. The resulting path of the selected waypoints are shown in the map in Fig. \ref{fig:map}, both within the expected frontal region (shaded pink region). The recorded temperatures are shown as colored trails in Fig. \ref{fig:res_both}, clearly showing the temperature difference between fjord and river waters. The salinity data are then shown separately overlaid with the estimated EP for each survey in Fig. \ref{fig:res1} and \ref{fig:res2}.

@@

This paper builds on multidisciplinary work combining statistical modeling and methods with robotic surveying technologies for oceanographic sensing applications. We show how the observation practices can gain from development of statistical techniques to achieve more effective spatial monitoring. We further demonstrate the opportunities available for real-time multivariable spatial data gathering and analysis onboard autonomous sensing platforms, upon which statisticians can exploit towards creating general-purpose toolkits for similar applications (enabeling theory).

>>>>

Two missions, Survey 1 and 2, were run successively from 11:00 AM to
01:00 PM \kc{date? month/year}, with a short break in between. The
resulting path of the selected waypoints are shown in the map in
Fig. \ref{fig:map}, both within the expected frontal region (shaded
pink region). The recorded temperatures are shown as colored trails in
Fig. \ref{fig:res_both}, clearly showing the temperature difference
between fjord and river waters. The salinity data are then shown
separately overlaid with the estimated EP for each survey in
Fig. \ref{fig:res1} and \ref{fig:res2}.

@@

This work builds on multidisciplinary work combining statistical
modeling and methods with robotic surveying technologies for
oceanographic sensing applications. We show how the observation
practices can gain from development of statistical techniques to
achieve more effective spatial monitoring. We further demonstrate the
opportunities available for real-time multivariable spatial data
gathering and analysis onboard autonomous sensing platforms, upon
which statisticians can exploit towards creating general-purpose
toolkits for similar applications (enabeling theory).
